Final Project Code ALL

### 2022-12-11 Draft_Final_Code.Rmd
Fixed degrees of freedom

```{r}
spline_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross) %>%
    step_ns(Runtime, deg_free = 19) %>%
    step_ns(No_of_Votes, deg_free = 9) %>%
    step_ns(IMDB_Rating, deg_free = 9)

>>>>

```{r}
spline_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross) %>%
    step_ns(Runtime, deg_free = 20) %>%
    step_ns(No_of_Votes, deg_free = 10) %>%
    step_ns(IMDB_Rating, deg_free = 10)
